### 2020-12-09 Thesis-Chapter4-Tools.tex
Work on DFD section and normalize captions

\begin{figure}[ht]
    \centering\CaptionFontSize
    \myincludeargument{demo}
    \caption[Argdown Demo]{A demonstrative example of argument maps with Argdown.}
    \label{fig-args-demo}
\end{figure}

@@

\Acp{DFD} are one tool designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and
external entities. \Acp{DFD} are well suited for threat modeling because security vulnerabilities tend to follow data
flow, not control flow \cite{shostack_threat_2014}. They are particularly well suited for \ac{EA}, as data privacy is of
primary concern. \myfig{fig-dfd-demo} shows the basic elements of a \ac{DFD}. In \mychap{chap-threatmodel} I create
\acp{DFD} in this style to analyze the threats already present and those that \ac{EA} would introduce.

\begin{figure}[ht]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/DFD-demo.png}
    \caption[\Acs{DFD} Demo]{A demonstrative example of a \acf{DFD}.}
    \label{fig-dfd-demo}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering\CaptionFontSize
    \myincludeargument{demo}
    \caption{A demonstrative example of argument maps with Argdown}
    \label{fig-args-demo}
\end{figure}

@@

\Acp{DFD} are one tool designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and
external entities. \Acp{DFD} are well suited for threat modeling because security vulnerabilities tend to follow data
flow, not control flow \cite{shostack_threat_2014}. They are particularly well suited for \ac{EA}, as data privacy is of
primary concern. \myfig{fig-dfd-dh-traditional} shows the basic elements of a \ac{DFD} of a simplified Diffie-Hellman
key exchange.

\begin{figure}[p]
    \centering\CaptionFontSize
    \includegraphics[width=0.8\linewidth]{dfds/build/diffie-hellman-traditional.png}
    \caption{A \acf{DFD} for a simplified Diffie-Hellman key exchange}
    \label{fig-dfd-dh-traditional}
\end{figure}

\Acp{DFD} show what data is transferred via labels on the flows. However, labels can be insufficient in complex
\acp{DFD}, and the method has no syntax for computation or cryptographic protocols. In order to maximize their
communicative ability in the context of encryption and \acl{EA} schemes, I introduce the additional syntax show in
\myfig{fig-dfd-dh-updated}.

\begin{figure}[p]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{dfds/build/diffie-hellman.png}
    \caption{A Diffie-Hellman key exchange illustrated with additional syntax}
    \label{fig-dfd-dh-updated}
\end{figure}

The new syntax illustrates the data in more detail as it is stored, transferred, and operated on. By illustrating the
data itself, it eliminates the need for labels on lines and can be used to communicate entire protocols in a single
% diagram. \myfig{fig-dfd-key} contains the full set of symbols. In \mychap{chap-threatmodel} I create \acp{DFD} in this
style to analyze the threats already present and those that \ac{EA} would introduce.

% \begin{figure}[p]
%     \centering\CaptionFontSize
%     \includegraphics[width=\linewidth]{dfds/build/dfd-key.png}
%     \caption{A Diffie-Hellman key exchange illustrated with additional syntax}
%     \label{fig-dfd-key}
% \end{figure}
